MWA tied-array processing III: Microsecond time resolution via a synthesis filter

### 2019-10-22 ipfb.tex
Fixed a typo or two, and added a placeholder image for the filter coefficients
Added the filter coefficients figure for real
Fixed another typo in one of the equations
A few tweaks to the existing text, for clarity

@@

The first stage (coarse) PFB is described in \citet{Prabu2015}, and here we only document a few details pertaining to the second stage (fine) PFB.
A PFB is completely specified by (1) the number of output channels, $N$, (2) the number of taps, $P$, and (3) the analysis filter, $h[m]$, $0 \le m < M=NP$.
For the MWA, $N=128$ (giving fine channels $10\,$kHz wide), $P=12$, and
\begin{equation}
    h[m] = w_H[m]\,w_s[m],
    \label{eqn:filter}
\end{equation}
where
\begin{equation*}
    w_H[m] = \sin\bigg(\frac{\pi (m+1)}{M+1}\bigg)
\end{equation*}
is the Hanning window, and
\begin{equation*}
    w_s[m] = \sin\bigg(\frac{\pi(m + 1 - M/2)}{N}\bigg)
\end{equation*}
is the stretched $\sinc$ function.
It can be easily checked that $h[m]$ is defined to be symmetric around sample $m = 767 = M/2-1$.

The above specifications yield a specific frequency response, as explained in the preceding section.
The rationale behind these particular design choices is beyond the scope of this paper---for the purposes of creating a synthesis filter, it is sufficient to know merely how the analysis filter is defined\footnote{Eq. \eqref{eqn:filter} is defined on $\mathbb{R}$, but the actual implementation on the MWA's filed-programmable gate arrays (FPGAs) defines the analysis filter coefficients on $\mathbb{Z}$. The exact implemented values of $h[m]$ can be obtained by the operation $h[m] \rightarrow \lfloor\alpha h[m]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}.

>>>>

% There is some ambiguity about whether this definition includes the correct set of phases, which differ depending on whether the filterbank is defined on [0,M) or [-M/2, M/2).
% It may turn out there is an extra phase ramp that's needed in Eq. \eqref{eqn:filter} below.
% See Harris et al. (2011) for a fuller discussion of this point.

@@

The first stage (coarse) PFB is described in \citet{Prabu2015}, and here we only document a few details pertaining to the second stage (fine) PFB.
A PFB is completely specified by (1) the number of output channels, $N$, (2) the number of taps, $P$, and (3) the analysis filter, $h[m]$, $0 \le m < M=NP$.
For the MWA, $N=128$ (giving fine channels $10\,$kHz wide), $P=12$, and
\begin{equation}
    h[m] = w_H[m]\,w_s[m],
    \label{eqn:filter}
\end{equation}
where
\begin{equation*}
    w_H[m] = \sin^2\bigg(\frac{\pi (m+1)}{M+1}\bigg)
\end{equation*}
is the Hanning window, and
\begin{equation*}
    w_s[m] = \sinc\bigg(\frac{\pi(m + 1 - M/2)}{N}\bigg)
\end{equation*}
is the scaled $\sinc(x) = \sin(x)/x$ function.
It can be easily checked that $h[m]$ is defined to be symmetric around sample $m = 767 = M/2-1$.
The analysis filter is shown in Fig. \ref{fig:filter}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{filter}
    \caption{The coefficients of the analysis filter defined in Eq. \eqref{eqn:filter}, composed of a Hanning window multiplied to a $\sinc$ function.}
    \label{fig:filter}
\end{figure}

The above specifications yield a specific frequency response, as explained in the preceding section.
The rationale behind these particular design choices is beyond the scope of this paper---for the purposes of creating a synthesis filter, it is sufficient to know merely how the analysis filter is defined\footnote{Eq. \eqref{eqn:filter} is defined on $\mathbb{R}$, but the actual implementation on the MWA's filed-programmable gate arrays (FPGAs) defines the analysis filter coefficients on $\mathbb{Z}$. The exact implemented values, $h^\ast[m]$, can be obtained from $h[m]$ via $h^\ast[m] \equiv \lfloor\alpha h[m]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}.
